Updates on the Exoplanet Orbit Database

### 2014-02-28 draft/ms.tex
Orbital parameters section revision 1

We report general information of when, by whom and how the planets were
discovered and provide the references. We describe the added fields since \cite{Wright2011} below. \\

@@

%------------------------------------------------------------------------------
\subsection{Orbit Parameters}
We report the orbit parameters that determine the shape of the planet's orbit. Depending on the detection methods, different parameters are given by the literatures. For instance, if a planet is detected by the radial velocity method, we get the semi-amplitude, whereas the transit method gives the inclination of the orbit.

{\bf MASS} is the mass of the planet in the unit of Jupiter mass. Previously, we only reported the minimum mass (MSINI) of the planets. We now report mass as well. If a planet is discovered by transit, the planet mass is given by the literature. However, if a planet is detected by radial velocity
method, the minimum mass is given in which case we calculate the mass
by dividing the minimum mass by the orbit inclination. MASS is set to
MSINI if the orbital inclination is not given and the MASSREF is set
to ``Set to MSINI; I unknown''. For KOIs without MSINI measured, the Exoplanet Archive reports MASS which is derived from the mass-radius relation.

>>>>

We report general information of when, by whom and how the planets were
discovered and provide the references. We describe the added fields since \cite{Wright2011} below.

@@

%------------------------------------------------------------------------------
\subsection{Orbital Parameters}
We report the orbital parameters that determine the shape of the planet's orbit. Depending on the detection methods, different sets of parameters are given by the literatures. For instance, if a planet is detected by the radial velocity method, the semiamplitude, $K$, is reported whereas the inclination of the orbit, $i$, is reported by the transit method.

We describe the added fields since \cite{Wright2011} below.

{\bf MASS} is the mass of the planet in the unit of Jupiter mass. Previously, we only reported the minimum mass, ($m\sin{i}$, MSINI) of the planets. We now report the mass as well. For example, if a planet is discovered by microlensing, we report the actual mass of the planet according to the literature. 
If a planet has both radial velocity and transit measurements, we calculate the mass from the minimum mass and the orbital inclination. MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''.

ZZZ For KOIs without MSINI measured, we import the MASS fields from the Exoplanet Archive, which are derived from the mass-radius relation in .
